Supplement to Faithful Variable Screening for\\ High-Dimensional Convex Regression

### 2015-12-07 tex/scam/supplement.tex
minor

\renewcommand{\baselinestretch}{1.00}
%\parskip12pt
%\parindent0pt
\setcounter{tocdepth}{2}

@@

\begin{supplement}
%\sname{Supplement A}
\stitle{Supplement to Faithful Variable Screening for High-Dimensional Convex Regression}
\slink[doi]{doi}
\sdatatype{.pdf}
\sdescription{We provide detailed proofs of certain technical results,
together with further explanation of the Gaussian example
and simplifications when the density is a product.}
\end{supplement}

>>>>

\renewcommand{\baselinestretch}{1.00}
%\parskip12pt
%\parindent0pt
\setcounter{tocdepth}{2}
\setattribute{journal}{name}{}

@@

\begin{frontmatter}
\title{Supplement to Faithful Variable Screening for\\ High-Dimensional Convex Regression}
\runtitle{Supplement to Faithful Variable Screening for Convex Regression}
\end{frontmatter}

In this supplement we provide detailed proofs of certain technical results,
together with further explanation of the Gaussian example
and simplifications when the density is a product.
